Enzo: An Adaptive Mesh Refinement Code for Astrophysics

### 2013-06-25 code-tests.tex
Edited section 11.1 and the overall Section 11 tex file (code-tests.tex).

Ensuring that a complex piece of software is behaving correctly is a
non-trivial task.  While there are a range of techniques that one can
apply to ensure correctness, the \enzo\ code uses two primary methods:
a suite of test problems that can be compared to previous versions of
the code, used to ensure that \enzo\ is running correctly on a new
computer, with a new compiler, or after substantial changes have been
made to the code base; and by direct comparisons to other
astrophysical fluid dynamics codes.  We describe the \enzo\ test
methodology in Section~\ref{sec.tests.suite}, code comparisons in
Section~\ref{sec.tests.compare}, and show a small set of
representative test problems in Section~\ref{sec.tests.problems}.  We
further note that the \enzo\ test suite
(Section~\ref{sec.tests.suite}) contains hundreds of test problems, as
well as the ability to compare to a ``gold standard'' solution, and
thus all of the tests shown here are easily reproducible by the
reader.

@@

The \enzo\ test suite (described in Section~\ref{sec.tests.suite})
contains hundreds of test problems that probe the code's behavior in a
wide range of physical circumstances, and explicitly test each physics
package in the \enzo\ code, both individually and in combination.  It
is impractical to include a substantial fraction of these problems in
a method paper; as a result, we have chosen to publish the results of
only a small subset of particularly crucial test problems here.  If
the interested reader desires, they can download \enzo\ and
\texttt{yt}, run the test suite, and see the results of any other test
problem and its comparison to an analytic solution (if available).

>>>>

Ensuring that a complex piece of software is behaving correctly is a
non-trivial task.  While there are a range of techniques that one can
apply to ensure correctness, the \enzo\ code uses two primary methods:
a suite of test problems that can be compared to previous versions of
the code, used to ensure that \enzo\ is running correctly on a new
computer, with a new compiler, or after substantial changes have been
made to the code base; and by direct comparisons to other
astrophysical fluid dynamics codes.  We describe the \enzo\ test
methodology in Section~\ref{sec.tests.suite}, discuss code comparisons
involving \enzo\ in Section~\ref{sec.tests.compare}, and show a small
set of representative test problems in
Section~\ref{sec.tests.problems}.  We further note that the \enzo\
test suite (Section~\ref{sec.tests.suite}) contains hundreds of test
problems, as well as the ability to compare to a ``gold standard''
solution, and thus all of the tests shown here are easily reproducible
by the reader.  To facilitate this, all of the test problems included
in this paper, as well as scripts to run the test problems and
generate the figures found in Section~\ref{sec.tests.problems}, can be
found on the \enzo\ website.

@@

The \enzo\ test suite (described in Section~\ref{sec.tests.suite})
contains hundreds of test problems that probe the code's behavior in a
wide range of physical circumstances, and explicitly tests each physics
package in the \enzo\ code, both individually and in combination.  It
is impractical to include a substantial fraction of these problems in
a method paper; as a result, we have chosen to publish the results of
only a small subset of particularly crucial test problems here.  If
the interested reader desires, they can download \enzo\ and
\texttt{yt}, run the test suite, and see the results of any other test
problem and its comparison to an analytic solution (if available), or
to a ``gold standard'' solution from a stable version of \enzo.

### 2013-06-25 tests-vandv.tex
Edited section 11.1 and the overall Section 11 tex file (code-tests.tex).

\enzo\ is capable of simulating a large variety of problems types,
with all but a few of these types requiring only a parameter file as an
input.  The notable exception is the cosmology simulation, which takes
as input initial conditions created by other codes.  The suite of test
problems spans a wide range in complexity.  At one end of this spectrum
are simple problems that utilize only a single component of \enzo\ and
for which analytic solutions exist for comparison with the simulation
results.  At the opposite end are problems that exercise a large
portion of \enzo's machinery in concert.  Together, the available
problem types fully cover all of \enzo's functionality.  This enables
them to serve as a vehicle for verifying that the code's behavior
remains stable over time and after modification of the codebase.

\enzo\ uses an automated testing framework that allows a user to run,
with a single command, a set of test problems and compare the results
against results produced by any other version of the code.  Within the
\enzo\ source distribution, the test problem parameter files are stored
in a nested directory structure organized according to the primary
functionality tested, e.g., hydrodynamics, gravity, cooling, etc.
Each parameter file is accompanied by a text file containing various
descriptive keywords, such as the machinery tested, the
dimensionality, and the approximate run time.  A test runner script is
responsible for taking as input from the user a series of keywords
that are used to select a subset of all available test problems.  The
test problems are also grouped into three suites: the quick, push, and
full suites, each a superset of the ones named before.  The quick
suite is considered to minimally cover the primary functionality in
\enzo\ and is designed to be run repeatedly during the development
process.  The push suite has slightly increased feature coverage and
is mandated to be run before code changes are accepted into the main
repository.  The full suite consists of all test problems that can be
run with no additional input.  Approximate run times for the quick,
push, and full suite are 15 minutes, 1 hour, and 60 hours,
respectively, on a relatively new desktop computer (circa 2013).

After the test problems are selected by the test runner script, they
are run in succession using either the \enzo\ executable contained
within that distribution or an external executable built from another \enzo\
version and specified by the user.  This allows for any version of the
code to be tested with an identical set of test problems.  After
running the test problem simulations, the test runner then performs a
series of basic analysis tasks using the \texttt{yt} analysis toolkit
\citep{2011ApJS..192....9T, 2011arXiv1112.4482T}.  The default
analysis performed on all test problems includes calculation of
various statistics, such as extrema, mean and variance, on the fields
present in the output data.  Custom analysis provided by scripts that
accompany the test problem parameter files is run for special cases,
such as when an analytical solution exists that can be compared
against the simulation data.  After the analysis is performed, the
results are compared against a set of gold standard results that are
maintained on a website and downloaded on the fly by the test runner
script.  Alternately, results from any version of \enzo\ can be stored
locally and compared to any other version of the code.  In
Section~\ref{sec.tests.problems}, we describe some of the key test
problems that are used to verify proper behavior.  All of these test
problems, as well as the scripts to generate the figures from them,
are available in the \enzo\ test suite, allowing the interested reader
to regenerate all of the figures in Section~\ref{sec.tests.compare}
using the \textit{`methodpaper'} suite of test problems.

>>>>

\enzo\ is capable of simulating a large variety of problems types,
with all but a few of these types requiring only a parameter file as an
input.  The most notable exception is the cosmology simulation, which takes
as input initial conditions created by other codes.  The suite of test
problems spans a wide range in complexity.  At one end of this spectrum
are simple problems that utilize only a single component of \enzo\ and
for which analytic solutions exist for comparison with the simulation
results.  At the opposite end are problems that exercise a large
portion of \enzo's machinery in concert.  Together, the available
problem types fully cover all of \enzo's functionality.  This enables
them to serve as a vehicle for verifying that the code's behavior
remains stable over time, on new computing platforms, and after modification of the codebase.

\enzo\ uses an automated testing framework that allows a user to run,
with a single command, a set of test problems and compare the results
against results produced by any other version of the code.  Within the
\enzo\ source distribution, the test problem parameter files are stored
in a nested directory structure organized according to the primary
functionality tested (e.g., hydrodynamics, gravity, cooling, etc.).
Each parameter file is accompanied by a text file containing various
descriptive keywords, such as the machinery tested, the
dimensionality, and the approximate run time.  A test runner script is
responsible for taking as input from the user a series of keywords
that are used to select a subset of all available test problems.  The
test problems are also grouped into three suites: the quick, push, and
full suites, each a superset of the ones named before.  The quick
suite is considered to minimally cover the primary functionality in
\enzo\ and is designed to be run repeatedly during the development
process.  The push suite has slightly increased feature coverage and
is mandated to be run before code changes are accepted into the main
repository.  The full suite consists of all test problems that can be
run with no additional input.  Approximate run times for the quick,
push, and full suite are 15 minutes, 1 hour, and 60 hours,
respectively, on a relatively new desktop computer (circa 2013).

After the test problems are selected by the test runner script, they
are run in succession using either the \enzo\ executable contained
within that distribution or an external executable built from another \enzo\
version and specified by the user.  This allows for any version of the
code to be tested with an identical set of test problems.  After
running the test problem simulations, the test runner then performs a
series of basic analysis tasks using the \texttt{yt} analysis toolkit
\citep{2011ApJS..192....9T, 2011arXiv1112.4482T}.  The default
analysis performed on all test problems includes calculation of
various statistics (such as extrema, mean, and variance) on the fields
present in the output data.  Custom analysis provided by scripts that
accompany the test problem parameter files is run for special cases,
such as when an analytical solution exists that can be compared
against the simulation data.  After the analysis is performed, the
results are compared against a set of gold standard results that are
maintained on a website and downloaded on the fly by the test runner
script.  Alternately, results from any version of \enzo\ can be stored
locally and compared to any other version of the code.  In
Section~\ref{sec.tests.problems}, we describe some of the key test
problems that are used to verify proper behavior.  All of these test
problems, as well as the scripts to generate the figures from them,
are available at \url{http://bitbucket.org/bwoshea/enzo-method-paper},
the Bitbucket repository for the \enzo\ method paper.  The
\texttt{test\_problems} subdirectory in this repository contains all of
the files necessary to regenerate all of the figures in
Section~\ref{sec.tests.problems}.  We note for completeness that 
the figures in Section~\ref{sec.tests.problems} were generated using \texttt{yt} version 2.5.3 and the
\url{https://bitbucket.org/enzo/enzo-dev} repository of \enzo\ with
changeset \texttt{5d8c412}.
